### 2014-03-30 doc/uist14/abstract.tex
smaller fixes, added area cusor refs

Emerging head-worn computing devices can enable hands-free interactions in physical spaces. 
%
We introduce and characterize a method for selecting and interacting with physical targets at a distance using head orientation. We augment a commercial wearable device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. The fundamental imprecision of head orientation requires a large selection beam \bjoern{term?} for successful target acquisition. However, a large beam area can lead to ambiguous selections. We introduce a two level disambiguation strategy: first, networked receivers use IR intensity sensors to estimate which target is the intended selection; second, users can fall back to a manual disambiguation technique using their near-eye display. The technique does not require an a priori map of target devices. However, a spatial data structure can be inferred to overcome sensor saturation problems in environments hostile to IR communication (e.g., in sunlight).
%
A target acquisition study with 14 participants shows that selection using head orientation with our device outperforms list selection on a wearable device. Intensity-based target disambiguation reduces selection time and error rate in dense target environments. We apply this technique to an application for controlling smart appliances and report qualitative usage data from a smart home scenario.

>>>>

Emerging head-worn computing devices can enable hands-free interactions in physical spaces. 
%
We introduce and characterize a method for selecting and interacting with physical targets at a distance using head orientation. We augment a commercial wearable device, Google Glass, with an infrared (IR) emitter to select targets equipped with IR receivers. The fundamental imprecision of head orientation requires area selection techniques, which can lead to ambiguous selections. We introduce a two level disambiguation strategy: first, networked receivers use IR intensity sensors to estimate which target is the intended selection; second, users can fall back to a manual disambiguation technique using their near-eye display. The technique does not require an a priori map of target devices. However, a spatial data structure can be inferred to overcome sensor saturation problems in environments hostile to IR communication (e.g., in sunlight). \bjoern{speculation, if we get to it}
%
A target acquisition study with 14 participants shows that selection using head orientation with our device outperforms list selection on a wearable device. Intensity-based target disambiguation reduces selection time and error rate in dense target environments. \bjoern{rewrite once we have results}. We implement this technique in an application for controlling smart appliances and report qualitative user impressions.
